\textbf{NBA Party}

### 2017-07-03 cardinal_analytx_presentation/nightlife_and_sports.tex
Added figure showing why drinking/population don't work, and additional details.

\begin{frame}   
  \frametitle{Who cares?}
  \begin{block}{\$400 billion spent on sports betting per year in the US.}
    Apparently, a lot of people.

@@

\begin{frame}   
  \frametitle{What is our solution?}
  \begin{block}{We can't observe whether players party.}
    Instead, we consider a quasi-experiment.
    \begin{itemize}       \item Do teams play worse the day after visiting a ``party city''?
      \item How do we even determine whether a city has nightlife?     \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}   \frametitle{Quasi Experiment}
  \begin{block}{Consider games played back-to-back within 24 hours.}     If odds of beating the spread uncorrelated with next day opponent 
    $\longrightarrow$ identification.

  (Under an efficient market, this should be the case)    \end{block}  
\end{frame}

@@

\begin{frame}   \frametitle{Bureau of Labor Statistics Data: 2010-2016}
  We look toward BLS data which describes the number of sound recording
  studios, musical groups, and musical publishers in each metropolitan statistical area
  for each quarter of each year.

@@

  These two locations are excluded from our analysis. \end{frame}

@@

\begin{frame}   \frametitle{Feature Creation}
  We add features which describe
  \begin{itemize}     \item Number of days since the last game (i.e. rest-time),
    \item Lagged game location, and
    \item Travel Distance.   \end{itemize}
  We seek to construct a model which accounts for travel-fatigue and jet-lag.
  For this, we need a little bit more. \end{frame}

@@

\begin{frame}   \frametitle{Future Research (General)}
  \begin{itemize}     \item It's possible there are prolonged effects; recall our magic 24 hour number.
    \item European soccer leagues.   \end{itemize} \end{frame}

@@

>>>>

\begin{frame}   
  \frametitle{Who cares?}
  \begin{block}{\$400 billion spent on sports betting per year in the US.\footnote{NBA Commissioner Adam Silver}}

    Apparently, a lot of people.

@@

\begin{frame}   \frametitle{Is the problem hard?}
  Yes, in general finding arbitrage opportunities is hard.

  Further, it's not obvious that we will find an effect. \end{frame}

\begin{frame}   
  \frametitle{What is our solution?}
  \begin{block}{We can't observe whether players party.}
    Instead, we consider a quasi-experiment. Motivating questions:
    \begin{itemize}       \item Do teams play worse the day after visiting a ``party city''?
      \item How do we even determine whether a city has nightlife?    
      \item What does it mean to ``play worse''? \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}
  \centering   \includegraphics[scale=0.55]{../writing/meet_the_spread} \end{frame}

\begin{frame}   \frametitle{Quasi Experiment}
  \begin{block}{Consider games played back-to-back within 24 hours.}     
    If next day opponent is uncorrelated with visitation to a party city $\leadsto$ identification.

    Weaker, still: if odds of beating the spread uncorrelated \\
    $\leadsto$ identification.\footnote{Under an efficient market, the latter assumption should hold.}    \end{block}  
\end{frame}

@@

\begin{frame}   \frametitle{Bureau of Labor Statistics Data: 2010-2016}
  We look toward BLS data which describes the number of business establishments 
  (of a very particular type) in each metropolitan statistical area
  for each quarter of each year.

@@

  These two teams are excluded from our analysis.\footnote{We don't expect Toronto to be a huge party city.} \end{frame}

@@

\begin{frame}   \frametitle{Feature Creation}
  We add features which describe
  \begin{itemize}     
    \item Number of days since the last game (i.e. rest-time),
    \item Lagged changes in possession,
    \item Lagged game location, and
    \item Travel Distance.   
  \end{itemize}
  We seek to construct a model which accounts for travel-fatigue and jet-lag.
  For this, we need a little bit more. \end{frame}

@@

\begin{frame}   \frametitle{Future Research (General)}
  \begin{itemize}     \item Possibly prolonged effects; recall our magic 24 hour number.
    \item European soccer leagues.   \end{itemize} \end{frame}

@@

\begin{frame}   \frametitle{Why \# Drinking Establishments or Population won't work}
  \includegraphics[scale=0.3]{../writing/why_drinks_or_population_dont_work} \end{frame}
